Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-11 cordillera-cycle.tex
Update contiguous ice sheet duration.

During most of the glacial cycle, modelled ice cover is restricted to disjoint
ice caps centred on major mountain ranges of the North American Cordillera
(Fig.~\ref{fig:duration}). A~contiguous ice cover spanning from the Alaska
Range to the Rocky Mountains exists for about 28\,\unit{kyr} in the GRIP
simulation and for about 29\,\unit{kyr} in the EPICA simulation. These values
represent cumulative ice cover over the two glaciations during MIS~2 and MIS~4,
while a dynamically consistent Cordilleran ice sheet forms for even shorter
time spans.

@@

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           A contiguous ice cover spanning from the Alaska Range (AR) to the
           southern Coast Mountians (CM) and Rocky Mountains (RM) exists for
           about 28\,\unit{kyr} in the GRIP simulation and about 29\,\unit{kyr}
           in the EPICA simulation. Note the irregular colour scale. A central
           ice cover persists over the Skeena Mountains (SM) during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           generally corresponds to relatively short durations of ice cover.}
  \label{fig:duration}
\end{figure}

>>>>

During most of the glacial cycle, modelled ice cover is restricted to disjoint
ice caps centred on major mountain ranges of the North American Cordillera
(Fig.~\ref{fig:duration}). In both the GRIP and the EPICA simulation,
a~contiguous ice cover spanning from the Alaska Range to the Rocky Mountains
exists for about 29\,\unit{kyr}. This value represent cumulative ice cover over
the two glaciations during MIS~2 and MIS~4, while a dynamically consistent
Cordilleran ice sheet forms for even shorter time spans.

@@

% fig:duration
\begin{figure}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,\unit{kyr}.
           Note the irregular colour scale. A contiguous ice cover spanning
           from the Alaska Range (AR) to the southern Coast Mountains (CM) and
           Rocky Mountains (RM) exists for about 29\,\unit{kyr} in both
           simulations. A central
           ice cover persists over the Skeena Mountains (SM) during most of the
           simulation. On the other hand, the maximal extent of the ice sheet
           generally corresponds to relatively short durations of ice cover.}
  \label{fig:duration}
\end{figure}
